---
title: "Class 11: Structural Bioinformatics 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The PDB database for biomolecular structure data

> Q1: Determine the percentage of structures solved by X-Ray and Electron Microscopy. 

> Determine what proportion of structures are protein? 

Download CSV file from PDB website ("Analyze > "PDB Statistics" > "by Experimental Method and Molecular Type")

```{r}
# Read CVS
data <- read.csv("Data Export Summary.csv",row.names = 1)
data
```

Total number of entries
```{r}
sum(data$Total)
```

Proportion of entries from each method
```{r}
#Percentages of structures solved by X-Ray and Electron Microscopy
data$Total / sum(data$Total)* 100

#Proportion of structures are protein
round((sum(data$Proteins)/sum(data$Total))*100,2)
#use round to restrain the number of significant figures to 2 figures 
```

## HIV-Pr structure analysis

Here we will read the 1HSG PDB structure and select the protein component and write out a new 

```{r}
library(bio3d)

pdb <- read.pdb("1hsg.pdb")
pdb
#read.pdb()
#atom.select()
#write.pdb()
#trim.pdb()
```


```{r}
ligand <- atom.select(pdb, "ligand", value = TRUE)
write.pdb(ligand, file ="1hsg_ligand.pdb")
```

















