---
title: "class08"
author: "Yutong Wu"
date: "10/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# K-means clustering 
```{r}
# Generate some example data for clustering
tmp <- c(rnorm(30,-3), rnorm(30,3))
rnorm(30,-3)
tmp
# rnorm(30,-3) -->30 points with mean of -3 
x <- cbind(x=tmp, y=rev(tmp))
x
plot(x)
```

Use the Kmeans() function setting k to 2 and nstart=20
```{r}
k <- kmeans(x, centers = 2, nstart =20)
```

Inspet/print the results
```{r}
k
```

Q. How many points are in each cluster? 30
Q. What 'component' of your result object details
    - cluster size?
    - cluster assignment/membership?
    - cluster center?
    
```{r}
k$size
```

```{r}
k$cluster
```

```{r}
k$centers
```

Plot x colored by the kmeans cluster assignment and add cluster centers as blue points

```{r}
plot(x, col=k$cluster)
#1 is black, 2 is red 
points(k$centers, col="blue", pch=15)
```

## Hierarchical clustering in R
The `hclust()` function requires a distance matrix as input. 
You can get this from the `dist()` function


```{r}
# First we need to calculate point (dis)similarity
# as the Euclidean distance between observations
dist_matrix <- dist(x)
#class(dist_matrix)

# The hclust() function returns a hierarchical
# clustering model
hc <- hclust(d = dist_matrix)

# the print method is not so useful here
hc

```

```{r}
# Our input is a distance matrix from the dist()
# function. Lets make sure we understand it first
dist_matrix <- dist(x) #dist() computes and returns the distance matrix 
dim(dist_matrix)
#NULL
View( as.matrix(dist_matrix) )
dim(x)
#[1] 60 2
dim( as.matrix(dist_matrix) )
#[1] 60 60
# Note. symmetrical pairwise distance matrix
```


```{r}
# Create hierarchical cluster model: hc
plot(hc)
abline(h=6,col="red")
grps <- cutree(hc,h=6)
#the fist 30 points are in the first big branch, the second 30 points are in the second branch 
```

```{r}
cutree(hc, k=2)
```

A more like real example 
```{r}
# Step 1. Generate some example data for clustering
x <- rbind(
matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2), # c1
matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
matrix(c(rnorm(50, mean = 1, sd = 0.3), # c3
rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y") #column names
# Step 2. Plot the data without clustering
plot(x)
# Step 3. Generate colors for known clusters
# (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
#rep(c("c1","c2","c3"),each=50)
plot(x, col=col)
```

```{r}
#create kmeans model and hierarchical model using R
kmeans(x,centers=3,nstart=20)
hclust(dist(x))
```
Q. Use the dist(), hclust(), plot() and cutree()
functions to return 2 and 3 clusters
Q. How does this compare to your known 'col' groups?

```{r}
# clustering
hc <- hclust(dist(x))

# draw tree
plot (hc)
abline(h=2, col = "red")

# Cut the tree into clusters/groups
grps <- cutree(hc,h=2.5)
grps
table(grps)
```


Plot the 
```{r}
table(grps)
```


Cross-tablulate i.e. compare out clustering result with the known answer 
```{r}
table(grps, col)
```

#Principal Component Analysis (PCA)
```{r}
## You can also download this file from the class website!
mydata <- read.csv("https://tinyurl.com/expression-CSV",
row.names=1)
head(mydata)
```

```{r}
dim(mydata)
nrow(mydata)
```




```{r}
## lets do PCA
pca <- prcomp(t(mydata), scale=TRUE)
## See what is returned by the prcomp() function
attributes(pca)

## A basic PC1 vs PC2 2-D plot
```


```{r}
plot(pca$x[,1], pca$x[,2])
## Variance captured per PC
pca.var <- pca$sdev^2
## Precent variance is often more informative to look at
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100, 1)
pca.var.per
```



```{r}
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100, 1)
barplot(pca.var.per, main="Scree Plot",
xlab="Principal Component", ylab="Percent Variation")
```

```{r}
plot(pca$x[,1], pca$x[,2],
     col = c("red", "red", "red", "red", "red","blue", "blue", "blue", "blue", "blue"))
```



#Hands-on Worksheet

```{r}
x <- read.csv("UK_foods.csv", row.names = 1)
x
dim(x)
```

```{r}
View(x)
```

```{r}
barplot(as.matrix(x), beside=F, col=rainbow(nrow(x)))
```

```{r}
pairs(x, col=rainbow(10), pch=16)
```

```{r}
pca <- prcomp( t(x) )
summary(pca)
```

```{r}
plot(pca$x[,1], pca$x[,2])
```

















