---
title: "class06homework"
author: "Yutong Wu"
date: "10/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Install the **bio3d** package in Console for sequence and structure analysis.

```{r}
#install.packages("bio3d") in Console
```

# This is the originally supplied code snippets:

```{r}
library(bio3d) #call the functions in bio3d package
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

# Now here is the more robust and re-usable function: 
## This function can take any of the three listed input proteins and plot the effect of drug binding

```{r}
protein.plot <-function(x){
  s1 <- read.pdb(x) 
  s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
  s1.b <- s1.chainA$atom$b
  plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
}
```

# Documentation:

**Input to the function:**
Input to the function is the Protein Data Bank (PDB) coordinate file of a specific protein/kinase
  
**What the function does:** 
The function takes the PDB coordinate file of a specific protein/kinase, trims it into a smaller PDB object that contain a subset of atoms by selecting a specific alpha strand on a specific chain (Chain A) of the protein/kinase, then assigns a variable that indicates file information particularly describing atom position b at Chain A of the kinase, finally draw a line plot of this variable/information

**How to use this function:**
Simply type the code protein.plot(), put the PDB file name of the target kinase within parenthases

**Output of the function:**
Output of the function is the line plot that describes atom postion b at Chain A of the specific kinase input, with optional secondary structure in the marginal regions.


# Now we try to use this function with the three kinase inputs:

```{r}
protein.plot("4AKE")
protein.plot("1AKE")
protein.plot("1E4Y")
```









