---
title: "Class 7 R functions and packages"
author: "Yutong Wu"
date: "10/22/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#R functions revisited 

Source my functions from last day

```{r}
source("http://tinyurl.com/rescale-R")
```


```{r}
rescale(1:10)
```

```{r}
rescale(c(1,10,5,NA,6))
```

!is.numeric()
! flips the logical value output from the function 


## A new function called both_na()
Write a function to find where there re NA elements in two input vectors.

First makes some simple inuput hwere I know the answers.

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
```

Looked online and found the **is.na()** function 
```{r}
is.na(x)
```

and the **which()** function tells me where the TRUE values are 
```{r}
which(is.na(x))
```

```{r}
which(is.na(y))
```

```{r}
is.na(x)
is.na(y)
```

The AND function requries two input TRUE to give a TRUE output 
```{r}
is.na(x) & is.na(y)
```

Taking the **sum()** of TRUE FALSE vector will tell me how many TRUE elements I have. 
This is my working snippet!
```{r}
sum(is.na(x) & is.na(y))
#TRUE represents 1 in R and FALSE equals 0
```

```{r}
#TRUE represents 1 in R and FALSE equals 0
```

Now turn it into a function.
```{r}
both_na <- function (x,y) {
  sum(is.na(x) & is.na(y))
}
```

```{r}
both_na(x,y)
```

```{r}
x <- c(1, NA, NA)
y1 <- c( 1, NA, NA)
y2 <- c( 1, NA, NA, NA, NA, NA, NA)
both_na(x,y2)
both_na(x,y1)
```

Show how R recycles 
```{r}
plot(1:10, col=c("red","blue","green"))
```

```{r}
length(x)
length(y2)
```


```{r}
both_na <- function (x,y) {
  
  if (length(x)!= length(y)) {
    z <- length (x) != length(y)
    stop("Inputs x and y should be the same length!")
  }
  sum(is.na(x) & is.na(y))
}
```



```{r}
x1 <- c(100, 100, 100, 100, 100, 100, 100, 90,100)
x2 <- c(100, NA, 90, 90, 90, 90, 97, 80)
x3 <- c(100, 100, 100, 100, 100, 100, 100,90,100,NA)
z <- length (x1) != length(x2)
z
```

```{r}
grade <- function (x) {
  if (sum(is.na(x)) > 0) {
    return(x[-which(is.na(x))])
  }
  min <- min(x)
  x[-which.min(x)]
}
```


```{r}
grade(x1)
grade(x3)
```

```{r}
which.min(x2)
x2[-which.min(x2)]
mean(x2[-which.min(x2)], na.rm = TRUE)
```

```{r}
any(is.na(x2))
any(is.na(x1))
```


We have our working code now turn it into a first function
```{r}
grade <- function(x) {
  if (any(is.na(x))) {
    warning("Student is missing a homework")
  }
  mean ( x[-which.min(x)], na.rm=TRUE)
}
  
```

```{r}
grade(x1)
```
```{r}
grade(x2)
```


```{r}
url <- "https://tinyurl.com/gradeinput"
hw <- read.csv(url, row.names=1)

hw
```

```{r}
apply(hw,1,grade)
#1 represents row, 2 represents column
```

```{r}

#student 1
x <- c(100, 100, 100, 100, 100, 100, 100, 90)
# student 2
y <- c(100, NA, 90, 90, 90, 90, 97, 80)

grade <- function(x){
  if(sum(is.na(x))>0)
  x <- x[-which(is.na(x))]
  
x <- x[-min(x)]
sum(x)
}

grade(y)
```

```{r}
library(BiocManager)
BiocManager::install("DESeq2")
library("DESeq2")
```


















